---
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE)

# necessary packages

library(tidyverse)
library(infer)

# loading data because I need that

tidy_int_reg_bag <- read_csv("all_tidy.csv",
                             col_types = cols(col_date(format = ''),
                                             col_character(),
                                             col_character(),
                                             col_character(),
                                             col_character(),
                                             col_character(),
                                             col_double()))

```

## Simulated Percentage of Interhouse Swipes Compared to Actual Percentage of Interhouse Swipes

### Model Explanation

Each distribution in the below plot represents the hypothetical distributions of interhouse swipes if each house had an equal chance of observing any percentage of interhouse swipes from the data. In other words, I randomly assigned houses to the observed percentages of interhouse swipes and then plotted the resulting distributions. These distributions represent what the interhouse swipe percentages would look like if each house had an equal probability of observing the different percentages of interhouse swipes from our data. The vertical lines for each plot represent the true percentage of interhouse swipes for each house over the two academic years. The distance from the vertical line and the distribution illustrates how far each house's percentage of interhouse swipes lies from average.

To get into more detail, I first calculated the percentage of interhouse swipes out of total swipes for every house on each date in the dataset. Then, I ran a bootstrapped random sample of the dataset, drawing 1,000 replicates of samples of size 372 * 12 (the total number of dates in the dataset multiplied by the total number of houses). After drawing these samples, I randomly assigned a house to each percentage of interhouse swipes. Then, I found the average percentage of interhouse swipes for each house within each replicate. Each plot displays the hypothetical distribution of the average percentage of interhouse swipes of the 1,000 replicates for the respective house.

```{r data_and_graph}

# first I want to find how many total interhouse diners there are on any given
# day in each house (all three meals). there are 372 unique dates in my data
# set, so I want to randomly selected that many rows multiplied by 12 (the total
# number of houses) for each replicate and then randomly assign a house to each
# proportion.

set.seed(2019)
nreps <- 1000

# I just want the upperclassmen houses, so I will remove those that are not. I
# need to create this vector so that I can randomly assign houses to percentages
# in the near future.

houses <- tidy_int_reg_bag %>% 
  select(house) %>% 
  filter(house != "Hillel",
         house != "FlyBy",
         house != "Annenberg") %>% 
  unique() %>% 
  pull()

pct <- tidy_int_reg_bag %>% 
  filter(type %in% c("int", "grand_total"),
         house != "Hillel",
         house != "FlyBy",
         house != "Annenberg") %>% 
  group_by(date, type, house) %>% 
  summarise(day_total = sum(count, na.rm = TRUE)) %>% 
  pivot_wider(names_from = type, values_from = day_total) %>% 
  mutate(pct_int = int / grand_total * 100) %>% 
  group_by(house) %>% 
  mutate(actual_pct_int = mean(pct_int))

pct %>% 
  select(house, date, pct_int, actual_pct_int) %>% 
  rep_sample_n(size = 372 * 12, replace = TRUE, reps = nreps) %>% 
  ungroup() %>% 
  mutate(houses = sample(houses, size = nrow(.), replace = TRUE)) %>% 
  
  # now I'm grouping by replicate and house to find the average percent of
  # interhouse diners in each house for each replicate
  
  group_by(replicate, houses) %>% 
  summarise(avg_pct_int = mean(pct_int, na.rm = TRUE)) %>% 
  
  # will add a column with the true average percentage of interhouse diners from
  # the original dataset so I can easily plot a vertical line on each of the
  # histograms that I'm about to generate
  
  mutate(actual_pct_int = pct %>% 
           group_by(house) %>% 
           summarise(actual_pct_int = mean(pct_int, na.rm = TRUE)) %>% 
           pull(actual_pct_int)) %>% 
  
  # next, I want to plot the values for each house on a histogram, with a
  # vertical line for the actual percent of interhouse diners for each house
  
  ggplot(aes(avg_pct_int, fill = houses)) +
  geom_histogram(bins = 50) +
  facet_wrap(~ houses) +
  geom_vline(aes(xintercept = actual_pct_int)) +
  
  
  # now adding/fixing labels to make the plot more appealing
  
  labs(title = "Bootstrapped Percentages of Interhouse versus Actual Percentages",
       fill = "Houses",
       subtitle = "Vertical Line Represents Each House's True Percentage of Interhouse Swipes") +
  ylab("Count") +
  xlab("Simulated Median Percentage of Interhouse Swipes")
  
  


```


## Discussion

### River Central

River Central is the only neighborhood where all of its houses have a greater percentage of interhouse swipes than average. This relative anomaly makes sense because of the neighborhood's relative proximity to the center of campus. For the 2017-2018 and 2018-2019 academic years, Lowell dining took place in the "Lowtel" swing housing facility just outside the gates of Tercentenary Theater. This location, as well as Adams and Quincy only require a few minutes of walking for those coming from class in the Yard or Tercentenary Theater. I hypothesize that the majority of interhouse swipes at these three locations came from students living in other housing neighborhoods. Students in these houses might as well walk to their own house, but the relative proximity of River Central houses makes any of them extra alluring to students from other neighborhoods

### The Quad

Not surprisingly, Cabot and Pforzheimer have a significantly smaller percentage of interhouse swipes than if these percentages were randomly assigned. Somewhat surprisingly, however, Currier has a greater than average percentage of interhouse swipes. I hypothesize that Currier interhouse swipes largely come from other Quad residents. Students living in the Quad have already made the hike home to their own house. However, they may have a preference for Currier's allegedly "superior" dining facility and food quality since it definitely is not a convenient location. Students living in Currier often do boast that their dining hall reigns supreme to all others, and this data point seems to confirm that Currier's dining is more desirable than the other Quad houses.

### River East

Winthrop appears to be students' top choice when they are dining in River East. While Kirkland has the closes location to the Yard, students may opt for Winthrop because the new renovations add a sense of novelty to the experience.

### River West

Following the theme seen in River East, Dunster has the greatest percentage of interhouse swipes out of the three River West Houses and it is the only with a percentage that is either at or above average for interhouse swipes. Potentially the newly renovated houses do indeed attract more interhouse diners. The trend seems to hold true for Winthrop and Dunster, so this is something to keep an eye on in future years for Lowell and Adams following the conclusion of renovations.